Modular flow and holographic entanglement entropy in cutoff AdS

### 2021-06-17 alpha/CutoffModularFlow/draft1.tex
Update conventions for cutoff mod flow note

\subsection{Rindler map in finite temperature}
	One can use the method in (1909.13808) to calculate the entanglement entropy in the thermal case and finite size case from the field theory side. The Rindler transformation from the domain of dependence of the interval $(-l_p,l_p)$ to the sphere is
	\begin{equation}
	t=l_p\frac{\sin\theta \sinh(\tau/l_p)}{1+\sin\theta \cosh(\tau/l_p)},\ \  x=l_p\frac{\cos\theta}{1+\sin\theta\cosh(\tau/l_p)}
	\end{equation}
	the conformal factor reads,
	\begin{equation}
	\Omega=\frac{1}{1+\sin\theta\cosh(\tau/l_p)}
	\end{equation}
	At endpoints, it becomes $1$. From the discussion in (1909.13808), the contribution to the entanglement entropy totally comes from the endpoints of the interval, so one can use the such conformal transformation where the conformal factor at the endpoints is $1$ to calculate the entanglement entropy. Also, in the conformal map above from the casual diamond to the sphere, only the length of the interval matters. If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $(0,\pm l_p)$, since the $T\bar T$ deformed theory also admits these symmetries. Now let's consider the thermal case, the conformal transformation from the thermal cylinder to the plane reads,
	\begin{equation}
	z=\frac{1}{ir_1}e^{ir_1w},\ \ \ r_1=\frac{2\pi}{\beta}
	\end{equation} 
	where $z$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
	\begin{equation}
	w\sim w+\beta
	\end{equation}
	The endpoints of the interval on the thermal cylinder is
	\begin{equation}
	w=\pm l i
	\end{equation} 
	The length of the interval is $L=2l$. Under the conformal map, the endpoints on the plane is
	\begin{equation}
	\frac{1}{ir_1}e^{\mp r_1 l}
	\end{equation}
	the length is $\frac{2}{r_1}\sinh(l r_1)$, so
	\begin{equation}
	l_p=\frac{1}{r_1}\sinh(l r_1)
	\end{equation}
	The conformal factor is
	\begin{equation}
	e^{ir_1(w+\bar{w})}
	\end{equation}
	Note that compared to the usual map from cylinder to plane $z=e^{ir_1 w}$, we put the overall scaling factor $\frac{1}{ir_1}$ to make sure that the conformal factor at the endpoints is $1$. From 1806.07444, the entanglement entropy for $l_p$ is
	\begin{equation}
	S_p(l)=\frac{c}{3}ArcSinh\frac{l_p}{a}
	\end{equation}
	where
	\begin{equation}
	a^2=\frac{\mu c}{12}
	\end{equation}
	The C-function reads,
	\begin{equation}
	C(L)=L S'(L=2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
	\end{equation}
	Now in the thermal case, $l_p\rightarrow \frac{1}{r_1}\sinh(l r_1)$
	\begin{equation}
	S_t=\frac{c}{3}ArcSinh(\frac{1}{r_1 a}\sinh(l r_1))
	\end{equation}
	which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation\eqref{}. Now consider the finite size case, the conformal transformation is,
	\begin{equation}
	z=\frac{1}{r_1}e^{wr_1}
	\end{equation}
	where $w$ is the cylinder coordinate,
	\begin{equation}
	w\sim w+i{\color{red} R}
	\end{equation}
	The endpoints of the interval are 
	\begin{equation}
	w\pm i l
	\end{equation}
	The conformal factor is
	\begin{equation}
	e^{r_1(w+\bar{w})}
	\end{equation}
	which is $1$ at the endpoints. The plane length reads,
	\begin{equation}
	l_p=\frac{1}{r_1}\sin lr_1
	\end{equation}
	So the final result is
	\begin{equation}
	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
	\end{equation}
	The global AdS reads,
	\begin{equation}
	 ds^2=-(r^2+1)dt^2+\frac{dr^2}{r^2+1}+r^2d\phi^2,\ \ \phi\sim\phi+2\pi
	\end{equation}
	\begin{equation}
	\phi\rightarrow r1\phi,\ \ r\rightarrow \frac{r}{r_1}, \ \ \ t\rightarrow r_2 t
	\end{equation}
	\begin{equation}
	 ds^2=-(r^2+r_1^2)dt^2+\frac{dr^2}{r^2+r_1^2}+r^2d\phi^2,\ \ \phi\sim\phi+\beta
	\end{equation}
	Compared to the planer BTZ,
	\begin{equation}
	ds^2=-(r^2-r_1^2)dt^2+\frac{dr^2}{r^2-r_1^2}+r^2dx^2
	\end{equation}
	For the holographic entanglement entropy
	\begin{equation}
	r_1\rightarrow ir_1
	\end{equation}
	There is no topological obstacle in global AdS, so one can do the replacement above to get the holographic entanglement entropy in global AdS from the HEE in planer BTZ.
	\begin{equation}
	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
	\end{equation}

@@

\subsubsection{Zero temperature: cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}

>>>>

\subsection{Rindler map in finite temperature}
	One can use the method in (1909.13808) to calculate the entanglement entropy in the thermal case and finite size case from the field theory side. The Rindler transformation from the domain of dependence of the interval $(-l_p,l_p)$ to the sphere is
	\begin{equation}
	t=l_p\frac{\sin\theta \sinh(\tau/l_p)}{1+\sin\theta \cosh(\tau/l_p)},\ \  x=l_p\frac{\cos\theta}{1+\sin\theta\cosh(\tau/l_p)}
	\end{equation}
	the conformal factor reads,
	\begin{equation}
	\Omega=\frac{1}{1+\sin\theta\cosh(\tau/l_p)}
	\end{equation}
	At endpoints, it becomes $1$. From the discussion in (1909.13808), the contribution to the entanglement entropy totally comes from the endpoints of the interval, so one can use the such conformal transformation where the conformal factor at the endpoints is $1$ to calculate the entanglement entropy. Also, in the conformal map above from the casual diamond to the sphere, only the length of the interval matters. If these two endpoints lie at other position, one can use the rotation and translation symmetry to put it at $(0,\pm l_p)$, since the $T\bar T$ deformed theory also admits these symmetries. Now let's consider the thermal case, the conformal transformation from the thermal cylinder to the plane reads,
	\begin{equation}
	z=\frac{1}{r_1}e^{r_1w},\ \ \ r_1=\frac{2\pi}{\beta}
	\end{equation} 
	where $z$ is the coordinate on the plane, and $w$ is the coordinate on the thermal cylinder with identification,
	\begin{equation}
	w\sim w+i\beta
	\end{equation}
	The endpoints of the interval on the thermal cylinder is
	\begin{equation}
	w=\pm l
	\end{equation} 
	The length of the interval is $L=2l$. Under the conformal map, the endpoints on the plane is
	\begin{equation}
	\frac{1}{r_1}e^{\pm r_1 l}
	\end{equation}
	the length is $\frac{2}{r_1}\sinh(l r_1)$, so
	\begin{equation}
	l_p=\frac{1}{r_1}\sinh(l r_1)
	\end{equation}
	The conformal factor is
	\begin{equation}
	e^{r_1(w+\bar{w})}
	\end{equation}
	Note that compared to the usual map from cylinder to plane $z=e^{r_1 w}$, we put the overall scaling factor $\frac{1}{r_1}$ to make sure that the conformal factor at the endpoints is $1$. From 1806.07444, the entanglement entropy for $l_p$ is
	\begin{equation}
	S_p(l)=\frac{c}{3}ArcSinh\frac{l_p}{a}
	\end{equation}
	where
	\begin{equation}
	a^2=\frac{\mu c}{12}
	\end{equation}
	The C-function reads,
	\begin{equation}
	C(L)=L S'(L=2l)=\frac{c}{3}\frac{1}{\sqrt{1+4a^2/L^2}}
	\end{equation}
	Now in the thermal case, $l_p\rightarrow \frac{1}{r_1}\sinh(l r_1)$
	\begin{equation}
	S_t=\frac{c}{3}ArcSinh(\frac{1}{r_1 a}\sinh(l r_1))
	\end{equation}
	which is the same as the results obtained from the local temperature trick \eqref{} and the gravity calculation \eqref{}. Now consider the finite size case, the conformal transformation is,
	\begin{equation}
	z=\frac{1}{ir_1}e^{iwr_1},\quad
		r_1 = \frac{2\pi}{\lambda}
	\end{equation}
	where $w$ is the cylinder coordinate,
	\begin{equation}
	w\sim w+ \lambda
	\end{equation}
	The endpoints of the interval are 
	\begin{equation}
	w\pm l
	\end{equation}
	The conformal factor is
	\begin{equation}
	e^{ir_1(w+\bar{w})}
	\end{equation}
	which is $1$ at the endpoints. The plane length reads,
	\begin{equation}
	l_p=\frac{1}{r_1}\sin lr_1
	\end{equation}
	So the final result is
	\begin{equation}
	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
	\end{equation}

	The global AdS reads,
	\begin{equation}
	 ds^2=-(r^2+1)dt^2+\frac{dr^2}{r^2+1}+r^2d\phi^2,\ \ \phi\sim\phi+2\pi
	\end{equation}
	\begin{equation}
	\phi\rightarrow r1\phi,\ \ r\rightarrow \frac{r}{r_1}, \ \ \ t\rightarrow r_2 t
	\end{equation}
	\begin{equation}
	 ds^2=-(r^2+r_1^2)dt^2+\frac{dr^2}{r^2+r_1^2}+r^2d\phi^2,\ \ \phi\sim\phi+\beta
	\end{equation}
	Compared to the planer BTZ,
	\begin{equation}
	ds^2=-(r^2-r_1^2)dt^2+\frac{dr^2}{r^2-r_1^2}+r^2dx^2
	\end{equation}
	For the holographic entanglement entropy
	\begin{equation}
	r_1\rightarrow ir_1
	\end{equation}
	There is no topological obstacle in global AdS, so one can do the replacement above to get the holographic entanglement entropy in global AdS from the HEE in planer BTZ.
	\begin{equation}
	S_f=\frac{c}{3}ArcSinh(\frac{1}{r_1a}\sin(lr_1))
	\end{equation}

@@

\subsection{Euclidean periodicity of the modular flow}
\subsubsection{Cutoff Poincar\'e $\mrm{AdS}_3$ and the loss of $2\pi$ periodicity}
